Unrestricted Termination and Non-Termination Arguments for Bit-Vector Programs

### 2015-04-13 slides/esop-termination.tex
Citation

\author{Cristina David \and Daniel Kroening \and Matt Lewis}
\title{Unrestricted Termination and Non-Termination Arguments for Bit-Vector Programs}
%\subtitle{}
\institute{Oxford University}
\date{\today}

@@

\begin{frame}{Example}
\end{frame}

@@

 These constraints can be solved using an EPR solver (such as the one in Z3), or by using a program
 synthesiser to synthesise $\red{F}$.
\end{frame}

@@

\subsection{Using Tautologies}

\begin{frame}{The Power of Tautologies}
 Our second-order solver works by trying to synthesise programs for each of the existentially quantified functions.

 This problem is NEXPTIME-hard, but in practice is quite fast if there is some short program that satisfies
 the constraints.

 However if the constraints are UNSAT, the solver will take a very long time to discover this.
\end{frame}

\begin{frame}{The Power of Tautologies}
 For a given loop, the formula \red{[CT]} is satisfiable iff the loop terminates and the formula \blue{[SNT]} is
 satisfiable iff it does not terminate.  Therefore, the formula
 \[
  \red{\text[CT]} \vee \blue{\text[SNT]}
 \]
 is satisfiable for \emph{every} loop.

 Since our solver produces witnesses to show that a formula is satisfiable, it will terminate with enough
 information to check whether the \red{[CT]} or \blue{[SNT]} disjunct has been satisfied.

 This allows us to avoid the expensive case of having to check an UNSAT formula.
\end{frame}

@@

>>>>

\author{Cristina David \and Daniel Kroening \and Matt Lewis}
\title{Unrestricted Termination and Non-Termination Arguments for Bit-Vector Programs}
%\subtitle{}
\institute{University of Oxford}
\date{\today}

@@

@@

 We solve these constraints by using a program synthesiser to synthesise $\red{F}$\footnotemark.

 \footnotetext{David, Kroening, Lewis -- Second-Order Propositional Satisfiability, arXiv \vspace{1em}}
\end{frame}

@@

% \subsection{Using Tautologies}
% 
% \begin{frame}{The Power of Tautologies}
%  Our second-order solver works by trying to synthesise programs for each of the existentially quantified functions.
% 
%  \vspace{1em}
% 
%  This problem is NEXPTIME-hard, but in practice is quite fast if there is some short program that satisfies
%  the constraints.
% 
%  \vspace{1em}
% 
%  However if the constraints are UNSAT, the solver will take a very long time to discover this.
% \end{frame}
% 
% \begin{frame}{The Power of Tautologies}
%  For a given loop, the formula \red{[CT]} is satisfiable iff the loop terminates and the formula \blue{[SNT]} is
%  satisfiable iff it does not terminate.  Therefore, the formula
%  \[
%   \red{\text[CT]} \vee \blue{\text[SNT]}
%  \]
%  is satisfiable for \emph{every} loop.
% 
%  \vspace{1em}
% 
%  Since our solver produces witnesses to show that a formula is satisfiable, it will terminate with enough
%  information to check whether the \red{[CT]} or \blue{[SNT]} disjunct has been satisfied.
% 
%  \vspace{1em}
% 
%  This allows us to avoid the expensive case of having to check an UNSAT formula.
% \end{frame}

@@

\begin{frame}{Experiments}
